Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-06 paper/paper.tex
results from feature combination experiments

>>>>

\begin{table}\small\centering
\begin{tabular}{lrcc}
\textbf{Feature Group} & \multicolumn{1}{c}{\textbf{\# Params}} & \textbf{Accuracy (\%)} & \textbf{$\ell_2$} \\
\hline
\feat{POS} & 540,947 & 55.18 & 1.0 \\
+ \feat{FreqChar} & 1,036,871 & 79.55 & 1.0 \\ 
\quad + \feat{CharPrompt} & 2,111,175 & 79.82 & 1.0 \\ 
\qquad + \feat{Brown} & 5,664,461 & 81.09 & 1.0 \\
\end{tabular}
\caption{Dev set accuracy with \textsc{main} feature groups, added cumulatively. 
The number of parameters is always a multiple of 11 (the number of classes). 
Only $\ell_2$ regularization was used for these experiments; 
the penalty was tuned on the dev set as well.}\label{tbl:mainfeats}
\end{table}

\begin{table}\small\centering
\begin{tabular}{lrcc}
\textbf{Feature Group} & \multicolumn{1}{c}{\textbf{\# Params}} & \textbf{Accuracy (\%)} & \textbf{$\ell_2$} \\
\hline
\textsc{main} + \feat{Position} & 6,153,015 & 81.00 & 1.0 \\
\textsc{main} + \feat{PsvRatio} & 5,664,472 & 81.00 & 1.0 \\
\textsc{main} & 5,664,461 & 81.09 & 1.0 \\
\textsc{main} + \feat{DocLen} & 5,664,472 & 81.09 & 1.0 \\
\textsc{main} + \feat{Pron} & 5,664,736 & 81.09 & 1.0 \\
\textsc{main} + \feat{Punct} & 5,664,604 & 81.09 & 1.0 \\
\textsc{main} + \feat{Misspell} & 5,799,860 & 81.27 & 5.0 \\
\textsc{main} + \feat{Restore} & 5,682,589 & 81.36 & 5.0 \\
\textsc{main} + \feat{CxtFxn} & 7,669,684 & 81.73 & 1.0 \\
\end{tabular}
\caption{Dev set accuracy with \textsc{main} features plus additional feature groups, added independently. 
$\ell_2$ regularization was tuned as in \tref{tbl:mainfeats} (two values, 1.0 and 5.0, were tried for each 
configuration; more careful tuning might produce slightly better accuracy).
Results are sorted by accuracy; only three groups exhibited independent improvements over the \textsc{main} feature set.}\label{tbl:addfeats}
\end{table}
